### 2013-05-27 doc/pgas13/flat-combining.tex
Add 'correctness' argument, swap two paragraphs in FC section

@@

The cost of synchronizing remotely on a distributed data structure drives the design of the Grappa flat-combining. Instead of all of the workers on a core sending messages to do remote synchronization independently, flat-combining can allow all of the workers to share a single remote synchronization operation. In a way, the Grappa runtime is already reducing synchronization traffic when it aggregates small messages that are all going to the same destination. However, it doesn't know what the operations are doing, so it must still serialize, pack, transmit, perform the operation on the remote side, and send a response for each message. Flat combining is about ``teaching'' it how to more efficiently perform many operations remotely in certain special cases.

@@

\paragraph{Correctness}
\TODO{Make argument about how flat-combining does not break things: sync operations still serialized on head, no order between things happening in different workers/cores unless otherwise synchronized, serializability not broken by satisfying requests locally.}

>>>>

The cost of performing synchronization remotely on a distributed data structure motivates applying the flat-combining paradigm to Grappa data structures. Instead of all of the workers on a core sending messages to do remote synchronization independently, flat-combining can allow all of the workers to share a single remote synchronization operation. In a way, the Grappa runtime is already reducing synchronization traffic when it aggregates small messages that are all going to the same destination. However, it doesn't know what the operations are doing, so it must still serialize, pack, transmit, perform the operation on the remote side, and send a response for each message. Flat combining is about ``teaching'' it how to more efficiently perform many operations remotely in certain special cases.

@@

@@

\paragraph{Correctness}

It may not be immediately obvious why this two-level version of flat combining preserves sequential consistency. The combining operations that are performed locally among requests on a single core must preserve the illusion of sequential order; this is unchanged from shared-memory flat-combining. When combined operations are applied globally, they are serialized at the ``master'' core for a given synchronization context. The global order is essentially the concatenation of each core's serialized updates. In the case where operations are satisfied locally (by matching up with other local operations), by definition these must be independent of other operations, so they can conceptually be placed anywhere in the global ordering (or even ignored completely in the global ordering).

In the spirit of the Data-Race-Free-0 Model (guaranteeing sequential consistency for data-race free programs), operations on the global data structure are considered to be made atomic by a conceptual global ``lock'' on the data structure. Atomicity and freedom from data races in the case of multiple data structures and other synchronization must be guaranteed externally, just as in any multithreaded shared-memory program.
